Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-20 paper/paper.tex
style up figure captions

\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_overview_DMN.pdf}
  \caption{Neurobiological overview of the DMN with its key constituent nodes and their associated functional roles relevant in our functional account.
  \label{fig:neurobiological_overview_DMN}
\end{figure}
%
\subsection{The posteromedial cortex: global monitoring and information integration}
The midline structures of the DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are probably responsible for the highest turn-over
of glucose energy consumption \citep{raichle2001pnas}.
These metabolic characteristics go hand-in-hand with
functional neuroimaging analyses \citep{andrews2010} in
suggesting that the PMC and mPFC
potentially represent the functional backbone of the DMN.

@@

\subsection{Putting everything together}
The DMN is today known to consistently increase in neural
  activity when humans engage in goal-directed behavior that are detached from
  current sensory environment \citep{kenet2003spontaneously, fiser2004small}
  and it was proposed to be situated at the top of the functional network hierarchies
  \citep{carhart2010default, margulies2016situating}.
  Its putative involvement in thinking about the past,
  the future, and hypothetical possibilities
  appears to tie in with the implicit computation of
  action and state cascades as a function of what happened in the past.
  A policy represents the repertoire of possible actions
    on the world given a current state. It encodes the probabilites of
    choosing actions to be executed in a certain situation.
% Interactions between external and internal sources of
% information are probably commonplace during perception \citep{gershman2010learning}
The DMN may subserve
  constant exploration of possible future actions and their
  cumulative reward outcomes. Implicit computation of future choices
  provides an explanation for the
  evolutionary emergence and practical usefulness of mind-wandering
  in humans.
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_and_rl_overview_DMN.pdf}
  \caption{Neurobiological implementation of RL by the DMN...}
  \label{fig:rl_process_chart}
\end{figure}

@@

The proposed machine-learning perspective
on DMN biology is hence not only practically computable but
also yields falsifiable neuroscientific hypotheses.
%
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on this major brain network.
%
Ultimately,
the DMN can be viewed as a functional integrator
from the relatively recent events to anticipated upcoming events
in to constantly refine the organism's interaction with the world.

>>>>

\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_overview_DMN.pdf}
  \caption{\textbf{Default mode network: key functions.}
  Neurobiological overview of the DMN with its major constituent nodes and
  their associated functional roles relevant in our functional account.}
  \label{fig:neurobiological_overview_DMN}
\end{figure}
%
\subsection{The posteromedial cortex: global monitoring and information integration}
The midline structures of the DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are probably responsible for the highest turn-over
of glucose energy consumption \citep{raichle2001pnas}.
These metabolic characteristics go hand-in-hand with
functional neuroimaging analyses \citep{andrews2010} in
suggesting that the PMC and mPFC
potentially represent the functional backbone of the DMN.

@@

\subsection{Putting everything together}
The DMN is today known to consistently increase in neural
  activity when humans engage in goal-directed behavior that are detached from
  current sensory environment \citep{kenet2003spontaneously, fiser2004small}
  and it was proposed to be situated at the top of the functional network hierarchies
  \citep{carhart2010default, margulies2016situating}.
  Its putative involvement in thinking about the past,
  the future, and hypothetical possibilities
  appears to tie in with the implicit computation of
  action and state cascades as a function of what happened in the past.
  A policy represents the repertoire of possible actions
    on the world given a current state. It encodes the probabilites of
    choosing actions to be executed in a certain situation.
% Interactions between external and internal sources of
% information are probably commonplace during perception \citep{gershman2010learning}
The DMN may subserve
  constant exploration of possible future actions and their
  cumulative reward outcomes. Implicit computation of future choices
  provides an explanation for the
  evolutionary emergence and practical usefulness of mind-wandering
  in humans.
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_and_rl_overview_DMN.pdf}
  \caption{\textbf{Default mode network: reinforcement learning implementation.}
  Overview of how the constituent nodes of the DMN
  map onto computational components necessary for a Markov decision process.}
  \label{fig:rl_process_chart}
\end{figure}

@@

The proposed machine-learning perspective
on DMN biology is hence not only practically computable but
also yields falsifiable neuroscientific hypotheses.
%
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on this major brain network.
%
Ultimately,
the DMN can be viewed as a functional integrator
from the relatively recent events to anticipated upcoming events
to constantly refine the organism's interaction with the world.
